Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-11 paper.qmd
Updated Figure 15 labels and figure title

highd_error_2d_mnist <- error_df |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = sqrt_row_wise_tot_error)) +
  geom_point(alpha=0.2) +
  scale_colour_continuous_sequential(palette = "YlOrRd", n_interp = 20) +
  geom_rect(aes(xmin = 0.82, xmax = 0.92, ymin = 0.38, ymax = 0.58),
               fill = "transparent", color = "#000000", linewidth = 1) +
  geom_rect(aes(xmin = 0.9, xmax = 1, ymin = 1.25, ymax = 1.45),
               fill = "transparent", color = "#375cb1", linewidth = 1)  +
  geom_rect(aes(xmin = 0.35, xmax = 0.45, ymin = 0.55, ymax = 0.7),
               fill = "transparent", color = "#008000", linewidth = 1)  +
  geom_rect(aes(xmin = 0.7, xmax = 0.8, ymin = 0.25, ymax = 0.4),
               fill = "transparent", color = "#4c389a", linewidth = 1) +
  interior_annotation(label = "a", c(0.1, 1), cex = 2.5) +
  theme(legend.position = "none",
        aspect.ratio = 1,
        plot.margin = margin(0, 0, 0, 0),
        panel.spacing = unit(0, "pt"),
        axis.ticks.length = unit(0, "pt"),
        strip.text = element_blank(),   # Optional, if you're using facets
        axis.title = element_blank()   # Optional
        )
```

@@

```{r}
#| label: fig-model-error-mnist
#| fig-cap: "The $10\\text{-}D$ model error in \\gD{} layout of the MNIST digit 1 data shows a pattern. Most low model errors are distributed along the big non-linear cluster, while most large model errors are distributed along the small cluster. The images associated with large model errors shows different patterns of digit 1, some inside (e) the non-linear structure and others outside (d). Along the non-linear cluster, the angle of digit 1 changes (a-c)."
#| fig-pos: H
#| fig-width: 10
#| fig-height: 10
#| out-width: 100%

>>>>

highd_error_2d_mnist <- error_df |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = sqrt_row_wise_tot_error)) +
  geom_point(alpha=0.2) +
  scale_colour_continuous_sequential(palette = "YlOrRd", n_interp = 20) +
  geom_rect(aes(xmin = 0.82, xmax = 0.92, ymin = 0.38, ymax = 0.58),
               fill = "transparent", color = "#000000", linewidth = 1) +
  geom_rect(aes(xmin = 0.9, xmax = 1, ymin = 1.25, ymax = 1.45),
               fill = "transparent", color = "#375cb1", linewidth = 1)  +
  geom_rect(aes(xmin = 0.35, xmax = 0.45, ymin = 0.55, ymax = 0.7),
               fill = "transparent", color = "#008000", linewidth = 1)  +
  geom_rect(aes(xmin = 0.7, xmax = 0.8, ymin = 0.25, ymax = 0.4),
               fill = "transparent", color = "#4c389a", linewidth = 1) +
  interior_annotation(label = "a", c(0.08, 0.93), cex = 2) +
  theme(legend.position = "none",
        aspect.ratio = 1,
        plot.margin = margin(0, 0, 0, 0),
        panel.spacing = unit(0, "pt"),
        axis.ticks.length = unit(0, "pt"),
        strip.text = element_blank(),   # Optional, if you're using facets
        axis.title = element_blank()   # Optional
        )
```

@@

```{r}
#| label: fig-model-error-mnist
#| fig-cap: "The $10\\text{-}D$ model error in \\gD{} layout of the MNIST digit 1 data shows a pattern. Most low model errors are distributed along the big non-linear cluster, while most large model errors are distributed along the small cluster. The images associated with large model errors shows different patterns of digit 1, some inside (f) the non-linear structure and others outside (e). Along the non-linear cluster, the angle of digit 1 changes (b-d)."
#| fig-pos: H
#| fig-width: 10
#| fig-height: 10
#| out-width: 100%
